---
title: "Build analysis from Tom's"
output: html_notebook
---

The idea is to with minimal modification bring added value to submission.

Most of the data gets written back to the data folder as rds:
```{r}
rds_list <- gsub(".rds","",list.files(path=paste0(project_wd,"/data"),pattern="rds"))
rds_list
```

Load them all:
```{r}
for (filename in rds_list)
{assign(filename,readRDS(paste0(project_wd,"/data/",filename,".rds")))}
```

Get the ids in sample submission (last ten characters are the visit date of the restaurant):
```{r}
sample_sub_ids <- sample_submission %>%
                  select(id) %>%
                  mutate(id=substr(id,1,nchar(id)-11)) %>%
                  unique %>%
                  unlist
```

There are `r length(sample_sub_ids)` restaurants for which we want to predict visit volume.

These are all present in the modelling data, and only 18.27% is present in the relation with hpg data.
```{r}
sum(sample_sub_ids %in% unique(modelling_data_train$air_store_id))/
  length(sample_sub_ids)*100
sum(sample_sub_ids %in% unique(store_id_relation$air_store_id))/
  length(sample_sub_ids)*100
```

Since hpg is not available for all the restaurants in the submission. We could think of extending any added value of the ones present through location, and genre matching.

There are 34 genres in hpg:
```{r}
unique(hpg_store_info$hpg_genre_name)
```

But only 14 in air
```{r}
unique(air_store_info$air_genre_name)
```

Let's check if some genres are more popular at some periods of the year
```{r}
GenreDateVolumes <- air_visit_data %>%
  left_join(air_store_info,by=c("air_store_id")) %>%
  select(air_genre_name,visit_date,visitors) %>%
  mutate(visit_dt=lubridate::month(visit_date,label=T)) %>%
  group_by(visit_dt,air_genre_name) %>%
  summarise(Visits=sum(visitors))

```

Japanese food and bars seem to experience a drop during the last 6 months of the year, that italian/french cuisine do not seem to experience. Okonomiyaki and so tend to increase during that period.
```{r}
library(plotly)
p<- GenreDateVolumes %>%
  #group_by(visit_month) %>%
  #summarise(Visits=sum(Visits)) %>%
  #filter(Visits<50000, Visits>1000) %>%
ggplot(aes(visit_dt,Visits,col=air_genre_name)) +
  geom_point() +
  labs(y="Visits",x = "Date")
p <- ggplotly(p)
p
```

```{r}
#library(ggmap)
#Japan <- get_map("Japan",zoom=5)
library(leaflet)
```

```{r}
m <- leaflet()

store_points <- air_store_info %>%
  select(latitude,longitude)

#p <- ggmap(Japan)
m <- addTiles(m)
m <- addMarkers(m, lng=store_points$longitude[1],lat=store_points$latitude[1])
#p
m

```

